### 2017-12-15 Writing/disparity_review.tex
Added dimensions effect example

\section{Do the disparity metrics (or indices) really reflect variation in the studied phenomenon?}
Do the disparity metrics really reflect the variation in the hypothesis that are tested?
E.g. Are the variance/range based metrics a description of the ordination or the observed biological phenomenon (i.e. they are not including covariance and phylogenetic signal)
E.g. What does the average distance between species or from a point really convey? Is the distribution not more interesting?
Do we need more like metrics measuring explicitly what is tested in the hypothesis (rather than approximate it). For example, for competitive replacement, should we not measure whether group A occupies the same place as group B through time and whether that is due to competition or simply because any other place in the space cannot be occupied (and why are such spaces unoccupied)?

>>>>

\section{Do the disparity metrics (or indices) really reflect variation in the studied phenomenon?}
From the 230 papers analysed, we found 104 unique combination's of metrics to measure disparity (Fig. \ref{Fig:MethodsProportions}).
Commonly, these metrics are used to approximate the volume occupancy within the morphospace \citep{Wills2001,DonohueDim,diaz2016global}.

However, it has been shown that different metrics reacts differently depending on the dataset

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Figures/DimensionsEffect.pdf} 
\caption{Effect of the number of dimensions on different disparity metrics (note that the sum of variance is equal to the average squared pairwise distance in this case).}
\label{Fig:DimensionsEffect}
\end{figure}

Product of variance

Is disparity only relative?

Do the disparity metrics really reflect the variation in the hypothesis that are tested?
E.g. Are the variance/range based metrics a description of the ordination or the observed biological phenomenon (i.e. they are not including covariance and phylogenetic signal)
E.g. What does the average distance between species or from a point really convey? Is the distribution not more interesting?
Do we need more like metrics measuring explicitly what is tested in the hypothesis (rather than approximate it). For example, for competitive replacement, should we not measure whether group A occupies the same place as group B through time and whether that is due to competition or simply because any other place in the space cannot be occupied (and why are such spaces unoccupied)?
